H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-13 slides-agu/presentation.tex
Improve README text

\begin{frame}{Motivating Example}
  What to do after Sandy? \citep{CityofNewYork:2013uh}
  \begin{figure}
    \centering
    \includegraphics[height=0.3\textheight]{three-barriers.png}~
    \includegraphics[height=0.3\textheight]{flood-concept.png}
    \caption{
      A large, permanent project would lock in $\approx \$25 \text{billion}$ for fixed protection; a portfolio of smaller investments may be more flexible and adaptive.
    }
  \end{figure}
  \pause
  \begin{alertblock}{Scheduling and sequencing:}
    When (and how) to build a flexible portfolio vs mega-project
  \end{alertblock}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How to identify \& predict}
    cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
 \end{alertblock}
 \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \item estimation strategy
        \item structure of climate signal
      \end{itemize}
      \pause
      To analyze predictions, we assess the \emph{bias} and \emph{variance} of predicted flood occurrence.
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Bias-Variance-Sketch.pdf}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}{Motivating Example}
  What to do after Sandy? \citep{CityofNewYork:2013uh}
  \begin{figure}
    \centering
    \includegraphics[height=0.3\textheight]{three-barriers.png}
    \includegraphics[height=0.3\textheight]{flood-concept.png}
    \caption{
      A large, permanent structure (L) would lock in $\approx \$25 \text{billion}$; a portfolio of smaller investments (R) may be more flexible and robust.
    }
  \end{figure}
  \pause
  \begin{alertblock}{Scheduling and sequencing:}
    When (and how) to build a flexible portfolio vs mega-project
  \end{alertblock}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How to identify \& predict}
    cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
 \end{alertblock}
 \pause
  \begin{figure}
    \includegraphics[width=\textwidth]{flowchart.pdf}
  \end{figure}
  defining $P^* \def \mathbb{P} \qty(X > X^*)$, the insurance premium
  \begin{equation*}
    R = \mathbb{E}\qty[ P^*] + \lambda \mathbb{V} \qty[P^*]
  \end{equation*}
\end{frame}
